---
title: "Homework 5 | Onyeka Isamah | oi2142"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

# Problem 1

- Cleaning the data, creating `city_state` and  `resolution` variables:
```{r cleaning homicide data, message=FALSE}
homicide_df = read_csv("./homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")


```

The **raw data set** has **`r ncol(homicide_df)`** variables and  **`r nrow (homicide_df)`** observations. Variables include `uid`, `reported_date`, `victim_last`, `victim_first`, `victim_race`, `victim_age`, `victim_sex`, `city`, `state`, `lat`,`lon`, and `disposition`. 

- Focusing on Baltimore to estimate the proportion of unsolved homicides. 
```{r baltimore proportions}
baltimore_df =
  homicide_df %>% filter(city_state == "BaltimoreMD")


baltimore_summary = baltimore_df %>% summarize(
  unsolved = sum(resolution == "unsolved"),
  n = n()
)
 
baltimore_test = 
  prop.test(
   x = baltimore_summary %>% pull(unsolved),
   n=  baltimore_summary %>%pull(n))
 

baltimore_test %>% 
  broom::tidy() %>%  knitr::kable()
```
- Iterating across cities:


```{r creating function for propotional testing}
prop_test_function = 
  function(city_df) {
    
    city_summary = 
      city_df %>% 
      summarize(
      unsolved = sum(resolution == "unsolved"),
             n = n()
)
 
    city_test = 
      prop.test(
        x = city_summary %>% pull(unsolved),
        n =  city_summary %>%pull(n))
    
    return(city_test)
  }

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(
    city_state == "AlbuquerqueNM"
  ) %>%  prop_test_function()
```

- Iterating across all cities.
```{r using map to iterate prop test across cities}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))



```
### Plot showing estimates and confidence intervals
```{r plot with estimates and ci,echo=FALSE}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + geom_point() + geom_errorbar(aes(ymin = conf.low, ymax = conf.high ))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
```





# Problem 2 

```{r list files, echo=FALSE}
files = tibble(
files =  list.files("./data"))
```

Subjects in the control group seems to have steady observations over the  weeks. In comparison, the experimental arm appears to have rising observations over the course of the 8 weeks. Overall, the experimental group appears to have higher observations over time compared to the comparison group.

```{r,  echo=FALSE, message=FALSE}

files =  
  tibble (
    list.files("./data", full.names=TRUE,
             )) %>% 
      map_dfr( read_csv ) 
files$subject_id <- as.numeric(1:20)

files = files %>% 
  relocate(subject_id)

```



```{r, echo=FALSE}
data_new = 
  pivot_longer(
    files, 
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observations") %>% 
      mutate(
        arm = case_when(subject_id %in% 1:10 ~ 'control',
                        subject_id %in% 11:20  ~ 'experimental'),
                        arm = fct_reorder(arm, observations),
                                          week = as.numeric(week)) 
data_new %>% 
  ggplot(aes(x = week, y = observations, group = subject_id, color = subject_id)) + geom_path() + 
  labs(caption = "Observations on each subject over time") + facet_grid(~arm)

```
